Stats for the convergence paper

### 2020-01-05 models/gcm/gcm.Rmd
new figs
final submission

setwd('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/gcm')
```

@@

```{r }
source('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/functions/grabfunctions.R')

source('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/functions/grabdata.R')

lookup = read_csv('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019/models/gcm/feature_distance_lookup_tidy.txt')

@@

```{r create_lookup_table2, eval=F}
# of course, what I do above is not what I did in practice. in practice, I fit four different sets of words because I was in the process of figuring out what's going on and what I need. The first set had word pairs repeat several times because of a join. Etc.
# see pocketgcm_create_lookup_table.R

# I'm not sharing these files, but you can see the code here to get an idea.

# batch 1
distances1 = read_csv('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/out.txt', col_names = F)
names(distances1) = 'feature.distance'

pairs1 = read_delim('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/everybody.txt', '\t', col_names = F)
names(pairs1) = c('target', 'training')

@@

# batch 2
distances2 = read_csv('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/out2.txt', col_names = F)
names(distances2) = 'feature.distance'

pairs2 = read_delim('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/everybody2.txt', '\t', col_names = F)
names(pairs2) = c('target', 'training')

@@

# batch 3
distances3 = read_csv('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/out3.txt', col_names = F)
names(distances3) = 'feature.distance'

pairs3 = read_delim('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/everybody3.txt', '\t', col_names = F)
names(pairs3) = c('target', 'training')

@@

# batch 4
distances4 = read_csv('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/out4.txt', col_names = F)
names(distances4) = 'feature.distance'

pairs4 = read_delim('~/Work/NZILBB/convergence_esp/ESP2019/pocketgcm/Alignment/everybody4.txt', '\t', col_names = F)
names(pairs4) = c('target', 'training')

@@

@@

Our lookup table has been made. Let's hope it's not the way Joe Pesci was made in Goodfellas.

@@

Reviewer points out that we are tilting the field in the GCM's favour by restricting its training set to verbs that basically look exactly like the verb schemata we are interested in. One of their alternative suggestions is to keep Moder classes but include *all* regular verbs in the regular category.

@@

## 2c. Tuning s for the reviewer GCM

@@

## 3a. Fitting the reviewer GCM (I hope this catches on) on the ESP experiment

@@

>>>>

setwd('~/Github/RaczBecknerHayPierrehumbert2019/models/gcm')
```

@@

```{r }
source('Github/RaczBecknerHayPierrehumbert2019/functions/grabfunctions.R')

source('Github/RaczBecknerHayPierrehumbert2019/functions/grabdata.R')

lookup = read_csv('Github/RaczBecknerHayPierrehumbert2019/models/gcm/feature_distance_lookup_tidy.txt')

@@

```{r create_lookup_table2, eval=F}
# I did this in four batches originally as I was in the process of figuring things out.
# I'm not sharing these files, but you can see the code here to get an idea.

# batch 1
distances1 = read_csv('Github/convergence_esp/ESP2019/pocketgcm/Alignment/out.txt', col_names = F)
names(distances1) = 'feature.distance'

pairs1 = read_delim('Github/convergence_esp/ESP2019/pocketgcm/Alignment/everybody.txt', '\t', col_names = F)
names(pairs1) = c('target', 'training')

@@

# batch 2
distances2 = read_csv('Github/convergence_esp/ESP2019/pocketgcm/Alignment/out2.txt', col_names = F)
names(distances2) = 'feature.distance'

pairs2 = read_delim('Github/convergence_esp/ESP2019/pocketgcm/Alignment/everybody2.txt', '\t', col_names = F)
names(pairs2) = c('target', 'training')

@@

# batch 3
distances3 = read_csv('Github/convergence_esp/ESP2019/pocketgcm/Alignment/out3.txt', col_names = F)
names(distances3) = 'feature.distance'

pairs3 = read_delim('Github/convergence_esp/ESP2019/pocketgcm/Alignment/everybody3.txt', '\t', col_names = F)
names(pairs3) = c('target', 'training')

@@

# batch 4
distances4 = read_csv('Github/convergence_esp/ESP2019/pocketgcm/Alignment/out4.txt', col_names = F)
names(distances4) = 'feature.distance'

pairs4 = read_delim('Github/convergence_esp/ESP2019/pocketgcm/Alignment/everybody4.txt', '\t', col_names = F)
names(pairs4) = c('target', 'training')

@@

celex2 %>% filter(is.na(moder.training), category.training == 'regular')

@@

Our lookup table has been made.

@@

One could argue that we are tilting the field in the GCM's favour by restricting its training set to verbs that basically look exactly like the verb schemata we are interested in. One alternative suggestion is to keep Moder classes but include *all* regular verbs in the regular category.

@@

## 2c. Tuning s for the GCM with the larger regular training set

@@

## 3a. Fitting this second GCM on the ESP experiment

@@

We are done with the GCM fits on the data.

### 2020-01-05 models/paper/convergence_paper_models.Rmd
final submission

try(setwd('~/Work/NZILBB/RaczBecknerHayPierrehumbert2019'))
try(setwd('~/Github/RaczBecknerHayPierrehumbert2019'))
```

@@

```{r }
# source('functions/grabdata.R')

celex = read_csv('data/celex_verbs_with_categories_csv_fixed_moder.txt')

celex = celex %>% 
  select(
    present.o,
    present,
    moder,
    regular
  ) %>% 
  rename(
    word = present.o,
    disc.old = present
  ) %>%
  mutate(
    category = case_when(
      regular == 'Y' ~ 'regular',
      regular == 'N' ~ 'irregular'
    )
  )  %>% 
  filter(!is.na(category))

# fixing transcription

transcription.matcher = read_csv('data/transcription_matcher.txt')

celex = left_join(celex, transcription.matcher)

celex[celex$disc == 'riN',]

# test set
baseline = read_csv('data/convergence_paper_baseline_data.txt')

baseline.verbs = read_csv('data/baseline_verbs.txt')
# esp data
espdata = read_csv('data/convergence_paper_esp_data.txt')

# esp only post-test with gcm weights
test2 = read_csv('data/convergence_paper_esp_test2_predictions.txt')

# moving factors round
test2$lex_typicality = factor(test2$lex_typicality, levels = c('typical', 'random', 'atypical'))
test2$reg_rate = factor(test2$reg_rate, levels = c('nc', '-40%', '+40%'))
test2$baseline_av_z = scales::rescale(test2$baseline_av)
test2$pre_reg_av_z = scales::rescale(test2$pre_reg_av)
test2$baseline_av_c = test2$baseline_av - mean(test2$baseline_av)
test2$pre_reg_av_c = test2$pre_reg_av - mean(test2$pre_reg_av)

# lex typ: typical - random - reversed
# reg rate: nc - -40% - +40%
test2$lexical_typicality = test2$lex_typicality
test2$regularisation_rate = ifelse(
  as.character(test2$reg_rate) == 'nc', 'no change',
  as.character(test2$reg_rate)
  )
test2$regularisation_rate = factor(test2$regularisation_rate, levels = c('no change', '-40%', '+40%'))

@@

## jumping to Appendix E!

@@

## jumping to Appendix F; Table 12

@@

## jumping to Appendix F.2

>>>>

try(setwd('~/Github/RaczBecknerHayPierrehumbert2019'))
```

@@

```{r }
source('functions/grabdata.R')

@@

## jumping to SI section E!

@@

## jumping to SI section F; Table 12

@@

## jumping to SI section F.2
